### 2023-01-18 paper.tex
Feedback for Section VI

	The application itself, however, has some limitations with regard to additional functionalities. Though the repository is fully functional, the information stored in the repository can still be enhanced to add even more ready information to the researchers. Each version of a source file can be associated with its corresponding bytecode and ABI, for faster analysis of incremental changes to gas costs. Also the Solidity compiler versions can be retrieved from the file header and stored separately to enable querying for files with specific compiler Solidity versions.

	Limitations also arise from the crawling process, the most important one being the fact that the scraping is currently limited to Solidity. Although the data model stores strings and hence can handle any syntax and language, the database has been built with Solidity contracts in mind. However, as discussed before, the script can be extended to include other languages including letting the user decide their language of choice.

	It can be argued that a database containing files originating only from public repositories of GitHub may not be representative of the currently deployed smart contracts. As mentioned before, multiple block explorers are available that list deployed smart contracts. However, most of these block explorers do not make the source code of the contracts is publicly accessible, neither do they offer access to multiple versions of the same contract, a limitation which arises from the immutability of the blockchain. Under such circumstances, choosing GitHub is the logical choice since GitHub is the most popular among software development organizations, which makes it easier to assume that the code available on GitHub at least provides an estimation of deployed code. Similar approaches of using GitHub as a source of data for code mining algorithms can be found in literature\cite{schroder, dabic, yang}. However, usage of GitHub can lead to the inclusion of unfinished and untested source code in the repository, and as mentioned before, duplicate code, in the absence of a mechanism to properly handle forks.

>>>>

	The application itself, however, has some limitations with regard to additional functionalities. Though the repository is fully functional, the information stored in the repository can still be enhanced to add even more ready information to the researchers. Each version of a source file can be associated with its corresponding bytecode and ABI, for faster analysis of incremental changes to gas costs. Also, the Solidity compiler versions can\todo{Is this a ``can'' or a ``could''?} be retrieved from the file header and stored separately to enable querying for files with specific compiler Solidity versions.

	Limitations also arise from the crawling process, the most important one being the fact that the scraping is currently limited to Solidity. Although the data model stores strings and hence can handle any syntax and language, the database has been built with Solidity contracts in mind. However, as discussed before, the script can\todo{ditto} be extended to include other languages including letting the user decide their language of choice.

	It can be argued that a database containing files originating only from public repositories of GitHub may not be representative of the currently deployed smart contracts. As mentioned before, multiple block explorers are available that list deployed smart contracts. However, most of these block explorers do not make the source code of the contracts is publicly accessible\todo{Something is wrong here in the sentence structure}, neither do they offer access to multiple versions of the same contract, a limitation which arises from the immutability of the blockchain. Under such circumstances, choosing GitHub as a foundation for the Smart Contract Repository is the logical choice since GitHub is the most popular among software development organizations, which makes it easier to assume that the code available on GitHub at least provides an estimation of deployed code. Similar approaches of using GitHub as a source of data for code mining algorithms can be found in literature\cite{schroder, dabic, yang}.\todo{Broken reference} However, usage of GitHub can lead to the inclusion of unfinished and untested source code in the repository, and as mentioned before, duplicate code, in the absence of a mechanism to properly handle forks.
